Report on the Fourth Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE4)

### 2017-02-08 WSSSPE4_report/WSSSPE4_report.tex
added lightning talk refs to paper

>>>>

Intro and description.
A \textsuperscript{\textasteriskcentered} indicates which author presented the
lightning talk, for those with multiple authors.
\katznote{not sure enum list is right here}
\kylenote{I'm fine with itemize, but they were in a particular order, right?}
%
\begin{enumerate}
    \item \textbf{Shoaib Sufi: \emph{The Software Sustainability Institute Fellowship
    programme; supporting the social side of research software}}~\cite{Sufi:2016ws}.
    Description
    %Didn’t want to “preach” to the community, wanted to be integrated with the
    % community, hence the fellows programme. Five attending WSSSPE this year.

    \item \textbf{Sandra Gesing, Maytal Dahan, Linda B.~Hayden, Katherine Lawrence,
    Suresh Marru, Marlon Pierce, Nancy Wilkins-Diehr, and Michael Zentner:
    \emph{The Science Gateways Community Institute - Supporting Communities to
    Achieve Sustainability for Their Science Gateways}}~\cite{Gesing:2016ws}.
    Description

    \item \textbf{Karthik Ram\textsuperscript{\textasteriskcentered}, Noam Ross,
    and Scott Chamberlain: \emph{A model for
    peer review and onboarding research software}}~\cite{Ram:2016ws}.
    Description
    %Some people greatly encouraged to only submit to a journal code that has been peer reviewed

    \item \textbf{Frank Löffler and Steven Brandt\textsuperscript{\textasteriskcentered}:
    \emph{A vision of computing in 10+ years}}~\cite{Loffler:2016ws}.
    Description
    %“We (need to) decouple science from numerical methods and optimization” Hard open problem.

    \item \textbf{Daniel S.~Katz, Kyle E.~Niemeyer\textsuperscript{\textasteriskcentered},
    Arfon M.~Smith, and the FORCE11 Software Citation Working Group:
    \emph{Software Citation: Process, Principles, and Implementation}}~\cite{Katz:2016ws}.
    Description

    \item \textbf{Ray Idaszak\textsuperscript{\textasteriskcentered},
    David G.~Tarboton, Hong Yi, Michael Stealey,
    Pabitra Dash, Alva Couch, Daniel P.~Ames, Jeffery S.~Horsburgh, Tony Castronova,
    Jon Goodall, Mohamed Morsy, Venkatesh Merwade, Mauriel Ramirez, Tian Gan,
    Drew (Zhiyu) Li, Jeff Sadler, Shawn Crawley, Zhaokun Xue, Lan Zhao, Carol Song,
    Christina Bandaragoda: \emph{HydroShare - A Case Study in Software Engineering
    Best Practices and Culture Change for Developing Sustainable Community
    Software}}~\cite{Idaszak:2016ws}.
    Description

    \item \textbf{Lorraine Hwang\textsuperscript{\textasteriskcentered},
    Wolfgang Bangerth, Timo Heister, and Louise Kellogg:
    \emph{ASPECT: Hackathons as an Example of Sustaining an Open Source
    Community}}~\cite{Hwang:2016ws}.
    Description

    \item \textbf{Carole Goble: \emph{A Simple Profiling Framework for Software
    User-Producer Maturity Review}}~\cite{Goble:2016ws}.
    Description

    \item \textbf{Stephan Druskat: \emph{A proposal for the measurement and
    documentation of research software sustainability in interactive metadata
    repositories}}~\cite{Druskat:2016ws}.
    Description

    \item \textbf{Mistral Contrastin, Matthew Danish,
    Dominic Orchard\textsuperscript{\textasteriskcentered}, and
    Andrew Rice: \emph{Supporting software sustainability with
    lightweight specifications}}~\cite{Contrastin:2016ws}.
    Description

    \item \textbf{Alice Allen, Cecilia Aragon, Christoph Becker, Jeffrey Carver,
    Andrei Chiș, Benoit Combemale, Mike Croucher, Kevin Crowston, Daniel Garijo,
    Ashish Gehani, Carole Goble\textsuperscript{\textasteriskcentered},
    Robert Haines, Robert Hirschfeld, James Howison,
    Kathryn Huff, Caroline Jay, Daniel S.~Katz, Claude Kirchner, Kateryna Kuksenok,
    Ralf Lämmel, Oscar Nierstrasz, Matt Turk, Rob van Nieuwpoort, Matthew Vaughn,
    and Jurgen Vinju: \emph{``I solemnly pledge'': A Manifesto for Personal
    Responsibility in the Engineering of Academic Software}}~\cite{AAllen:2016ws}.
    Description

    \item \textbf{Eric L.~Seidel\textsuperscript{\textasteriskcentered}
    and Gabrielle Allen: \emph{Bringing Techniques from Software Engineering
    into Scientific Software}}~\cite{Seidel:2016ws}.
    Description
